StarCraft Bots and Competitions

### 2015-12-16 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
Add number of entrans and map pool for AIIDE 2011

In 2011 the University of Alberta hosted the competition, with organization by Michael Buro and
David Churchill\footnote{\url{https://skatgame.net/mburo/sc2011/}}. Due to a lack of entrants in tournament categories 1-3 in the 2010 competition, it was
decided that only the full game category would be played in the 2011 competition. Another important
change in the 2011 competition was the introduction of automated tournament-managing software running
StarCraft games simultaneously on 20 computers, allowing a total of 2340 games to be played in the five days that the tournament ran. 
This increase in games played also allowed the tournament
to switch to a round-robin format, eliminating the ``luck'' factor of the pairings inherent in bracket
style tournaments. The bot that achieved the highest win percentage over the course of the competition would
be determined the winner. Also, the competition became open-source, in an effort 
to prevent possible cheating and to promote healthy competition in future tournaments by giving
newcomers and easier entry point by basing their design off of previous bots.

>>>>

In 2011 the University of Alberta hosted the competition, with organization by Michael Buro and
David Churchill\footnote{\url{https://skatgame.net/mburo/sc2011/}}. Due to a lack of entrants in tournament categories 1-3 in the 2010 competition, it was
decided that only  the full game category would be  played in the 2011
competition, with 13 entrants. Another important
change in the 2011 competition was the introduction of automated tournament-managing software running
StarCraft games simultaneously on 20 computers, allowing a total of 2340 games to be played in the five days that the tournament ran. 
This increase in games played also allowed the tournament
to switch to a round-robin format, eliminating the ``luck'' factor of the pairings inherent in bracket
style tournaments. The bot that achieved the highest win percentage over the course of the competition would
be determined the winner. Also, the competition became open-source, in an effort 
to prevent possible cheating and to promote healthy competition in future tournaments by giving
newcomers  and  easier entry  point  by  basing  their design  off  of
previous bots. All  maps used by the competition were  known long time
by advance, so participants can test their bot on them.  These 10 maps
remains the same for all AIIDE  competition, from 2011 until the last
one  at the  time this  chapter  has been  written in  2015. Maps  are
\emph{(2)Benzene},    \emph{(2)Destination}, \emph{(2)HeartbreakRidge},  \emph{(3)Aztec},  \emph{(3)TauCross},  \emph{(4)Andromeda},
\emph{(4)CircuitBreaker}, \emph{(4)EmpireoftheSun}, \emph{(4)Fortress}
and \emph{(4)Python}. The number between  parenthesis is the number of
possible start points.
